
% Multiple abstracts on the same page
\newenvironment{abstractpage}
%{\cleardoublepage\vspace*{\fill}\thispagestyle{empty}}
%{\clearpage\vspace*{\fill}\thispagestyle{empty}}
{\vspace*{\fill}\thispagestyle{empty}}
%{\vspace*{\fill}}
{\vfill\clearpage}
\renewenvironment{abstract}[1]
{\bigskip\selectlanguage{#1}%
	\begin{center}\bfseries\abstractname\end{center}}
{\par\bigskip}

%\chapter*{Abstract \markboth{Abstract}{}}
\addcontentsline{toc}{chapter}{Abstract}
\begin{abstractpage}
	\begin{abstract}{english}
%		\addcontentsline{toc}{chapter}{Abstract (English)}
		For blood flow estimation, ultrasound imaging is an important tool. This project report outlines the design, implementation, and analysis of such ultrasound blood velocity estimator. The design is based off a central control system on a Xilinx Zynq 7000 SoC for generating ultrasound pulses and the various timing signals needed for operating the custom designed analogue front-end. The chosen design topology uses a pulsed-wave design with quadrature demodulation to obtain the Doppler frequency. The system was module tested, but was not fully end-to-end tested on a physiological simulator due to time constraints.
	\end{abstract}

	\begin{abstract}{danish}
%		\addcontentsline{toc}{chapter}{Abstract (Danish)}
        Til estimering af blodgennemstrømning er ultralydsbilledeanalyse et vigtigt værktøj. Denne projektrapport skitserer design, implementering og analyse af en sådan ultralyds-blodhastigheds-estimator. Designet er baseret på et centralt kontrolsystem på en Xilinx Zynq 7000 SoC til generering af ultralydspulser og de forskellige timingsignaler der er nødvendige, for at betjene det specialdesignede analoge interface. Den valgte designtopologi bruger en såkaldt pulsed-wave type samt kvadraturdemodulation for at få en lavfrekvent Doppler-frekvens. Systemet blev modultestet, men blev ikke fuldstændigt ende-til-ende-testet på en fysiologisk simulator grund af tidsbegrænsninger.
	\end{abstract}

	\begin{abstract}{korean}
%		\addcontentsline{toc}{chapter}{Abstract (Korean)}
		안녕하세요, 여기 의미 없는 문자가 있습니다. 이 텍스트는 이 플레이스에서 인쇄된 텍스트의 모양을 보여줘야 합니다. 이 텍스트를 읽으면 정보를 얻을 수 없습니다. 정말? 정보가 없나요? 이 텍스트와 "Huardest gefburn"과 같은 말도 안 되는 내용 사이에 차이가 있나요? Kjift – 전혀 그렇지 않습니다! 이와 같은 블라인드 텍스트는 선택한 글꼴, 글자의 작성 방법 및 모양에 대한 정보를 제공합니다. 이 텍스트는 알파벳의 모든 문자를 포함해야 하며 원래 언어로 작성되어야 합니다. 특별한 내용은 필요 없지만, 단어의 길이는 언어와 일치해야 합니다.
	\end{abstract}
\end{abstractpage}