%\thispagestyle{empty}
\thispagestyle{main}
\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
I would like to express my sincere gratitude to all those who have contributed to the completion of this thesis.

Firstly, I would like to thank my advisors, Lee Hyunjoo, Fontas, and Gabriel, for their guidance and support throughout the entire research process. Their valuable feedback and constructive criticism have been instrumental in shaping my ideas and improving the quality of my work.

Secondly, I would like to show my profound gratitude to Erick and Hyoga, with whom I shared the EE office, for graciously helping me catch up when I was overwhelmed with coursework. They dedicated their time to help me get up to speed, and I am truly thankful.

I would also like to extend my gratitude to all the members of Brain/Bio Medical Microsystems Laboratory, who have inspired me during my academic journey. Their kindness creates a positive atmosphere and their profound knowledge have provided me with a solid foundation for conducting research.

I am deeply grateful to my family and friends back home for their unwavering support and encouragement, both academically and personally. Their love, care, and motivation have kept me going during the challenging times of this project.

Finally, I would like to acknowledge the collaborative experiments done with Sangmok and Taemin, whose willingness to take part in this research has made it possible for me to generate meaningful findings. Their insights and experiences have been invaluable in helping me to answer my research questions.
